Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-26 paper/ICPC19/icpc19.tex
another update

\usepackage{pifont}
\newcommand{\lstbg}[3][0pt]{{\fboxsep#1\colorbox{#2}{\strut #3}}}
\lstset{ %
  language=Java,
  backgroundcolor=\color{white},   % choose the background color
  basicstyle=\ttfamily\scriptsize,        % size of fonts used for the code
  breaklines=false,                 % automatic line breaking only at whitespace
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygray}\bfseries,    % comment style
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  keywordstyle=\color{blue},       % keyword style
  stringstyle=\color{mymauve},     % string literal style
  frame=single,
  escapeinside={/*!}{!*/},
  morekeywords={@Override,@TargetApi},
  moredelim=**[l][\color{mygreen}]{+},
  moredelim=*[l][\color{red}]{-}
}

@@

%\lstinputlisting[language=Python]{source_filename.py}

>>>>

\newcommand{\lstbg}[3][0pt]{{\fboxsep#1\colorbox{#2}{\strut #3}}}
\lstset{ %
  language=C,
  backgroundcolor=\color{white},   % choose the background color
  basicstyle=\ttfamily\scriptsize,        % size of fonts used for the code
  breaklines=false,                 % automatic line breaking only at whitespace
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygray}\bfseries,    % comment style
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  keywordstyle=\color{blue},       % keyword style
  stringstyle=\color{mymauve},     % string literal style
  frame=single,
  escapeinside={/*!}{!*/},
  morekeywords={@Override,@TargetApi},
  moredelim=**[l][\color{mygreen}]{+},
  moredelim=*[l][\color{red}]{-}
}

@@

Improving energy efficiency of apps revolves around chang- ing their codebases. Previous work has studied existing energy patterns for mobile applications [18]. It cataloged typical coding practices developers adopt to address energy efficiency. An example of an energy pattern is the Power Save Mode: the app features a mode that can be activated upon low battery and uses fewer resources while providing the minimum
+ functionality that is indispensable to the user.

\begin{lstlisting}

+ static unsigned long dtls1_max_handshake_message_len(
+ 	const SSL *s)
+	{
+	unsigned long max_len = DTLS1_HM_HEADER_LENGTH + 
+ 			SSL3_RT_MAX_ENCRYPTED_LENGTH;
+	if (max_len < (unsigned long)s->max_cert_list)
+		return s->max_cert_list;
+	return max_len;
+	}

// [snip]

 	pitem *item = NULL;
 	int i = -1, is_complete;
 	unsigned char seq64be[8];
-	unsigned long frag_len = msg_hdr->frag_len, max_len;
-
-	if ((msg_hdr->frag_off+frag_len) > msg_hdr->msg_len)
-		goto err;
-
-	/* Determine maximum allowed message size. Depends on (user set)
-	 * maximum certificate length, but 16k is minimum.
-	 */
-	if (DTLS1_HM_HEADER_LENGTH + SSL3_RT_MAX_ENCRYPTED_LENGTH < s->max_cert_list)
-		max_len = s->max_cert_list;
-	else
-		max_len = DTLS1_HM_HEADER_LENGTH + SSL3_RT_MAX_ENCRYPTED_LENGTH;
+	unsigned long frag_len = msg_hdr->frag_len;

-	if ((msg_hdr->frag_off+frag_len) > max_len)
+	if ((msg_hdr->frag_off+frag_len) > msg_hdr->msg_len ||
+	    msg_hdr->msg_len > dtls1_max_handshake_message_len(s))
 		goto err;

// [snip]

 		if (frag_len && frag_len < msg_hdr->msg_len)
 			return dtls1_reassemble_fragment(s, msg_hdr, ok);

+		if (frag_len > dtls1_max_handshake_message_len(s))
+			goto err;
+
 		frag = dtls1_hm_fragment_new(frag_len, 0);
 		if ( frag == NULL)
 			goto err;

\end{lstlisting}
